---
title: 'Stats 250: Homework 1'
author: "Homework Team"
date: "September 4, 2020"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Homework assignments will typically contain a couple questions that test your ability to use R for data analysis. Each week, we will provide you with an R Markdown template (like this one) that you will use to alter or create code that generates some sort of desired output. This "desired output" might be in the form of a numerical summary, a table, a plot, or even the result of a statistical test. In order to 

### Ann Arbor Trees

We'll be using the Ann Arbor trees data set that we used in Lab 2. This data set contains information about a subset of the top nine types of trees planted around Ann Arbor in 2009. Check out Lab 2 if you'd like more information about the data set. Be sure to run the code chunk below to read in the data set.

```{r readData, error = T}
a2trees <- read.csv("a2trees_clean.csv")
```

#### Question 1

Create a bar chart for the `Place` variable in the `a2trees` data set. **Be sure to include a proper title and axis labels.**  

```{r placePlot, error = T}
# Feel free to copy, paste, and alter code from your Lab 1 or Lab 2 assignment! (Remember that this text is a comment, so R ignores it; you can delete it if you want. If you don't delete it, START CODE ON THE NEXT BLANK LINE)

```

To submit your completed plot, you can either:

- Right click on your plot and click "Save Image".

OR

- Take a screen shot of the plot (Mac users can hit "Command + Shift + 4" to take a select the portion of their screen to capture; Windows users can hit "Windows logo + Shift + S" to do the same).

Whichever you prefer! Then head to Course.Work and upload your saved image.


#### Question 2

Create a table for the variable `LandmarkTree` variable in the `a2trees` data set.  

```{r landmarkTable, error = T}
# Feel free to copy, paste, and alter code from your Lab 2 assignment! (Remember that this text is a comment, so R ignores it; you can delete it if you want. If you don't delete it, START CODE ON THE NEXT BLANK LINE)

```

To submit your completed table, you can either:

- Copy and paste the output into Course.Work (be careful of the text shifting when you paste it).

OR

- Take a screen shot of the plot (Mac users can hit "Command + Shift + 4" to take a select the portion of their screen to capture; Windows users can hit "Windows logo + Shift + S" to do the same). Then head to Course.Work and upload your saved image.
