---
title: 'Stats 250: Homework 2'
author: "Homework Team"
date: "September 11, 2020"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Homework assignments will typically contain a couple questions that test your ability to use R for data analysis. Each week, we will provide you with an R Markdown template that you will use to alter or create code that generates some sort of desired output. This "desired output" might be in the form of a numerical summary, a table, a plot, or even the result of a statistical test. 

<hr />

## Statistics Student Survey

This week, in preparation for your first MWrite assignment, we will use a data set constructed from a random sample from the Stats 250 Fall 2020 Student Survey (if you filled it out, you may be part of this dataset!). 

```{r readData, error = T}
stats250survey <- read.csv("mwrite_data.csv")
```

Let's check out a quick preview of the data set using the `head()` function.

```{r previewData, error = T}
head(stats250survey)
```

The data set `stats250survey` contains the following list of variables:

| Variable name | Description |
|:--------------|:----------------------------------------|
|`a2_return`| Returned to Ann Arbor for Fall 2020 (Yes, No) |
|`hometown_distance`| Distance between hometown residence and the Diag (in miles) |
|`residency_status`| U-M residency status (In-State, Out-of-State Domestic, International) |
|`class_standing`| Class standing (First Year, Sophomore, Junior, Senior, Other) |
|`transfer_student`| Transfer student (Yes, No) |
|`extroversion`| Self-described extroversion (Introvert, In Between, Extrovert) |


<hr />


## Homework Tasks

### Question 9a - Part 1 (Table)

Using the `stats250survey` data set, create a table for the response variable `a2_return` (the variable indicating whether the student returned to Ann Arbor for Fall 2020 or not). 

```{r a2returnTable, error = T}
# Feel free to copy, paste, and alter code from previous lab assignments! (Remember that this text is a comment, so R ignores it; you can delete it if you want. If you don't delete it, START CODE ON THE NEXT BLANK LINE)

```

To submit your completed table, you can either:

- Copy and paste the output into Course.Work (be careful of the text shifting when you paste it).

OR

- Take a screen shot of the plot (Mac users can hit "Command + Shift + 4" to take a select the portion of their screen to capture; Windows users can hit "Windows logo + Shift + S" to do the same). Then head to Course.Work and upload your saved image.



### Question 9a - Part 2 (Bar Chart)

Using the `stats250survey` data set, create a bar chart for the response variable `a2_return`. As a friendly reminder, your plot should include an appropriate title containing the type of plot produced, the variable plotted, and the your name or initials.

```{r a2returnBarChart, error = T}
# Feel free to copy, paste, and alter code from previous lab assignments! (Remember that this text is a comment, so R ignores it; you can delete it if you want. If you don't delete it, START CODE ON THE NEXT BLANK LINE)

```

To submit your completed plot, you can either:

- Right click on your plot and click "Save Image".

OR

- Take a screen shot of the plot (Mac users can hit "Command + Shift + 4" to take a select the portion of their screen to capture; Windows users can hit "Windows logo + Shift + S" to do the same).



### Question 9b - Part 1 (Exp Var 1)

In order to help you better understand how student characteristics have influenced their decision on whether or not they return to Ann Arbor for Fall 2020, you are asked to identify **two** explanatory variables of interest from the list of variables in the `stats250survey` data set.

Provide a table or graphical summary for the *first* explantory variable you selected. This table or graphical summary will help you explore the relationship between your first explanatory variable of interest and the response variable `a2_return`.

```{r stats250surveySummary1, error = T}
# Feel free to copy, paste, and alter code from previous lab assignments! (Remember that this text is a comment, so R ignores it; you can delete it if you want. If you don't delete it, START CODE ON THE NEXT BLANK LINE)

```

To submit a table, refer to the instructions in Question 9a - Part 1, above. To submit a plot, refer to the instructions in Question 9a - Part 2, above. 

### Question 9b - Part 2 (Exp Var 2)

Provide a table or graphical summary for the *second* explantory variable you selected. This table or graphical summary will help you explore the relationship between your second explanatory variable of interest and the response variable `a2_return`.

```{r stats250surveySummary2, error = T}
# Feel free to copy, paste, and alter code from previous lab assignments! (Remember that this text is a comment, so R ignores it; you can delete it if you want. If you don't delete it, START CODE ON THE NEXT BLANK LINE)

```

To submit a table, refer to the instructions in Question 9a - Part 1, above. To submit a plot, refer to the instructions in Question 9a - Part 2, above.

